Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples

### 2024-05-22 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd
fix path to heatmap
save copykat output

---
title: "Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  no_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/no_reference"
  with_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/with_reference"
---

@@

obj_file <- glue::glue("{params$library_id}_final-copykat.rds")
png_file <- glue::glue("{params$libary_id}_heatmap-copykat.png")

copykat_objs <- c(
  no_ref = file.path(params$no_ref_copykat_results, obj_file),
  with_ref = file.path(params$with_ref_coypkat_results, obj_file)
) |> 
  purrr::map(readr::read_rds)

png_list <- c(
  no_ref = file.path(params$no_ref_copykat_results, png_file),
  with_ref = file.path(params$with_ref_copykat_results, png_file)
)
```

@@

@@

cnv_df <- umap_df |> 
  # first add manual annotations
  dplyr::left_join(manual_classifications_df) |> 
  # now add copykat results
  dplyr::left_join(ck_results_df, by = c("barcodes" = "cell.names"))
```

@@

```{r}
filtered_cnv_df <- cnv_df |> 
  dplyr::filter(copykat.pred != "not.defined")

@@

>>>>

---
title: "Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  no_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/copykat/no_reference"
  with_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/copykat/with_reference"
  reference_cell_file: "../results/annotate_tumor_cells_output/SCPCS000490/annotations/SCPCL000822_reference-cells.tsv"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

@@

obj_file <- glue::glue("{params$library_id}_final-copykat.rds")
png_file <- glue::glue("{params$libary_id}_copykat_heatmap.jpeg")

copykat_objs <- c(
  no_ref = file.path(params$no_ref_copykat_results, obj_file),
  with_ref = file.path(params$with_ref_copykat_results, obj_file)
) |> 
  purrr::map(readr::read_rds)

png_list <- c(
  no_ref = file.path(params$no_ref_copykat_results, png_file),
  with_ref = file.path(params$with_ref_copykat_results, png_file)
)

# output classifications file 
copykat_results_file <- file.path(params$results_dir, glue::glue("{params$library_id}_copykat-classifications.tsv"))
```

@@

# read in ref cells 
normal_cells <- readr::read_tsv(params$reference_cell_file) |> 
  dplyr::filter(reference_cell_class == "Normal") |> 
  dplyr::pull(barcodes)

@@

cnv_df <- umap_df |> 
  # first add manual annotations
  dplyr::left_join(manual_classifications_df) |> 
  # now add copykat results
  dplyr::left_join(ck_results_df, by = c("barcodes" = "cell.names")) |> 
  dplyr::mutate(
    copykat.pred = dplyr::if_else(
      # label any reference cells that were used 
      (barcodes %in% normal_cells) & (reference_used == "with_ref"), 
      "reference", 
      copykat.pred)
  )
```

@@

```{r}
filtered_cnv_df <- cnv_df |> 
  dplyr::filter(!(copykat.pred %in% c("not.defined", "reference")))

@@

## Save annotations

```{r}
celltype_df <- cnv_df |> 
  dplyr::select(barcodes, 
                reference_used,
                copykat.pred) |> 
  dplyr::distinct() |> 
  tidyr::pivot_wider(
    names_from = reference_used,
    values_from = copykat.pred
  )

readr::write_tsv(celltype_df, copykat_results_file)
```
